\documentclass[11pt]{article}
\begin{document}
\thispagestyle{empty}

\begin{center}
\begin{large}
\textbf{Patrick Lam} \\
\textbf{Thoughts on New England Hiking} \\
\textbf{October 22, 2008}
\end{large}
\end{center}

``Well, I'm glad I don't have to hike that anymore!''

When thinking about hiking in New Hampshire, I recall expressing the
above thought a couple of times, particularly about the Lincoln Woods
Trail, even if the Bonds are superlative. Additionally, moving from
Boston to Montreal made the Vermont mountains more accessible than
before\footnote{Unfortunately, I'm now no longer near any mountains at
  all.}.  Plus, Maine is supposed to be nice; in any case, it had the
potential to be just a bit different from New Hampshire, and I like
new things.

Katahdin, of course, was awesome, and remote. Apart from Katahdin, I
did enjoy the slightly greener and less rocky Maine and Vermont
hikes. I must say that I did not enjoy the muddy August hiking on our
trip to the Rangeley-Stratton area. We also got to experience evenings
in Rangeley on that trip, an interesting experience. I now appreciate
general stores in New England a lot more than after New Hampshire
hiking, though! I feel that the Maine peaks are further off the beaten
track than the New Hampshire ones; they are further from Boston, for
sure (and closer to Montreal).

The bushwhack to Reddington from South Crocker was fairly
straightforward and well-worn; almost like a trail. We considered
bushwhacking on to Spaulding after Reddington, instead of returning to
the car and then out to Sugarloaf, but the bush between the logging
road and Spaulding looked impenetrable.

Of course, we referred to the Maine Mountain Guide in hiking the
Maine peaks. As a bit of a data freak, I would have liked having 
elevation gain numbers in the Maine Mountain Guide; apart from that,
the guide served its purpose quite well. 

\vspace*{1em}

I think that I'll give lists a break for a little while now, unless I
get tempted to hike the ADK 46ers (which are a bit closer to Waterloo,
Ontario, than New Hampshire; they're still quite far, though). I'll
probably do more rock climbing and less climbing in the future,
although who knows; I might find myself climbing some peaks in winter!

\end{document}
